
\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage[colorlinks=true,linkcolor=black,urlcolor=blue]{hyperref}
\usepackage{longtable}
\usepackage{array}
\usepackage{geometry}
\usepackage{tocloft}
\usepackage{fancyhdr}
\usepackage{lastpage}

\hypersetup{
    pdfborder={0 0 0},
    colorlinks=true,
    linkcolor=black,
    urlcolor=blue
}

\geometry{
  a4paper,
  left=1in,
  right=1in,
  top=1in,
  bottom=1in,
  headheight=14pt,
  headsep=0.5in,
  footskip=0.5in
}

\renewcommand{\cftsecleader}{\cftdotfill{\cftdotsep}}
\renewcommand{\cftsubsecleader}{\cftdotfill{\cftdotsep}}
\renewcommand{\cftsubsubsecleader}{\cftdotfill{\cftdotsep}}

\title{SUAS Software Requirements Specification (SRS)}
\author{SUAS Development Team}
\date{May 2025}

\begin{document}

\maketitle
\newpage

\tableofcontents
\newpage

\section*{Version History}
\begin{longtable}{| m{3cm} | m{3cm} | m{8cm} |}
\hline
\textbf{Version} & \textbf{Date} & \textbf{Description} \\
\hline
1.0 & 2025-05-07 & Finalized SRS incorporating all snapshot stages \\
\hline
0.9 & 2025-04-30 & Legal and data ethics considerations added \\
\hline
0.8 & 2025-03-30 & External interface requirements drafted \\
\hline
0.7 & 2025-02-28 & Initial draft with introduction \\
\hline
\end{longtable}

\section{Introduction}
\subsection{Purpose}
This Software Requirements Specification (SRS) defines the functional and non-functional requirements for the SUAS (Software Unmanned Aircraft System) application.

\subsection{Intended Audience}
This document is intended for stakeholders, developers, testers, and any personnel involved in maintaining or extending the software.

\subsection{Overview}
The SUAS application is designed to assist users in planning, simulating, and analyzing unmanned aerial missions through an intuitive software platform.

\section{External Interface Requirements}
\subsection{User Interface}
The user interface will include:
\begin{itemize}
    \item A dynamic map interface with waypoint dragging and creation.
    \item Panels showing real-time telemetry, mission status, and replay controls.
    \item Modal dialogs for configuring settings, mission parameters, and data exports.
\end{itemize}

\subsection{Software Interfaces}
The application will integrate with:
\begin{itemize}
    \item REST APIs to fetch weather and map data.
    \item PostgreSQL database to store mission configurations, logs, and telemetry.
    \item Simulation engines for mission preview and data replay.
\end{itemize}

\section{Legal and Ethical Considerations}
\subsection{User Data Protection}
All mission data, user settings, and telemetry will be stored securely using encryption and access control. The system will avoid collecting personally identifiable information unless explicitly authorized.

\subsection{Data Retention}
Stored data will include timestamps for deletion eligibility and will follow data minimization principles. Logs will be retained only as long as needed for mission auditing or debugging.

\subsection{Ethical Use}
The SUAS system is not intended for surveillance or any military use unless governed under explicit legal contracts. The software will include terms of use warning against misuse of UAV technology in protected or private areas.

\subsection{Moral Dilemmas}
The software will not make autonomous decisions regarding harm or privacy breaches. All mission actions must be user-confirmed, especially if flying over sensitive zones (e.g., schools, hospitals, private properties).

\end{document}
