
\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{hyperref}
\usepackage{tocloft}
\usepackage{fancyhdr}
\usepackage{lastpage}


\geometry{
  a4paper,
  left=1in,
  right=1in,
  top=1in,
  bottom=1in,
  headheight=14pt,
  headsep=0.5in,
  footskip=0.5in
}

\hypersetup{
    pdfborder={0 0 0},
    colorlinks=true,
    linkcolor=black,
    urlcolor=blue
}

\renewcommand{\cftsecleader}{\cftdotfill{\cftdotsep}}

\title{SUAS Project - Snapshot Objectives}
\author{SUAS Development Team}
\date{May 2025}

\begin{document}

\maketitle
\vspace{1cm}
\tableofcontents
\newpage

\section{Start Objective}
At the start of the SUAS project, the goal was to lay the foundation for all core systems. This included:
\begin{itemize}
    \item Setting up the development environment (Java, Spring Boot, PostgreSQL).
    \item Designing the system architecture for separation of concerns (frontend, backend, DB).
    \item Initializing the Git repository and setting up basic CI/CD (if applicable).
    \item Creating placeholder UIs for the dashboard and mission planner.
    \item Drafting initial versions of the SRS and SDD documents.
\end{itemize}

\section{1st Checkpoint Objective}
Reflection on the previous phase showed success in establishing the core application structure and working mission planning interface.

The new tasks introduced at this stage included:
\begin{itemize}
    \item Integrating pathfinding logic for automatic navigation.
    \item Adding data persistence for waypoints and mission objects.
    \item Updating UI to allow real-time path edits.
    \item Expanding SRS and SDD to reflect new functionalities.
    \item Creating TestRail test cases for path generation and saving.
\end{itemize}

\section{2nd Checkpoint Objective}
At this checkpoint, the simulation engine was implemented and telemetry logging was introduced.

New tasks added:
\begin{itemize}
    \item Building a simulation playback system using stored data.
    \item Implementing data charts for telemetry replay.
    \item Refining the mission planner UI for better usability.
    \item Finalizing most of the database schema.
    \item Updating snapshot documents and reflecting changes in design spec.
\end{itemize}

\section{Due Date Checkpoint}
By the project deadline, all core features were functional including:
\begin{itemize}
    \item Live mission planning and simulation playback.
    \item Stable backend and database interactions.
    \item UI workflows for mission creation and management.
    \item Full documentation: SRS, SDD, User Manual, Design Spec.
\end{itemize}

\textbf{Future Work:}
\begin{itemize}
    \item Integration with live drone APIs for real deployment.
    \item Advanced features like auto-collision detection.
    \item Support for multi-UAV mission coordination.
    \item Deployment pipeline using Kubernetes or cloud hosting.
\end{itemize}

\end{document}
