
\documentclass[12pt]{article}
\usepackage{geometry}
\usepackage{graphicx}
\usepackage{listings}
\usepackage{hyperref}
\usepackage{enumitem}
\geometry{margin=1in}

\title{SUAS Flight Path Visualization - Design Specification}
\author{Army Research Lab Project Team}
\date{\today}

\begin{document}

\maketitle

\section*{1. Overview}
This document describes the components, tools, and libraries required for the SUAS Flight Path Visualization web application. It also outlines each page and feature implemented in the system.

\section*{2. System Pages and Components}

\subsection*{2.1 Home Page}
\begin{itemize}
    \item Provides an overview and navigation to other components.
    \item Features a header, navigation bar, and short project description.
\end{itemize}

\subsection*{2.2 Flight Dashboard}
\begin{itemize}
    \item Real-time or simulated visualization of SUAS flight paths on a map.
    \item Map rendered with Leaflet.js or Mapbox GL JS.
    \item Data from backend APIs visualized as polylines and markers.
\end{itemize}

\subsection*{2.3 Mission Upload}
\begin{itemize}
    \item Allows uploading of mission files (JSON/CSV).
    \item Parses and stores waypoint data.
    \item Backend parsing with Python or Node.js.
\end{itemize}

\subsection*{2.4 Analytics and Telemetry}
\begin{itemize}
    \item Charts for speed, altitude, distance vs time.
    \item Implemented using Chart.js or D3.js.
\end{itemize}

\subsection*{2.5 Admin Panel}
\begin{itemize}
    \item For managing users, uploading test runs, and tracking system status.
    \item Protected with authentication (JWT/Session).
\end{itemize}

\section*{3. Technologies and Tools}

\subsection*{Frontend}
\begin{itemize}
    \item \textbf{React.js}
        \begin{itemize}
            \item Libraries: react, react-dom, react-router-dom, axios
        \end{itemize}
    \item \textbf{Bootstrap 5}
    \item \textbf{Chart.js} for plotting
    \item \textbf{Mapbox GL JS} or \textbf{Leaflet.js} for maps
\end{itemize}

\subsection*{Backend}
\begin{itemize}
    \item \textbf{Python Flask}
        \begin{itemize}
            \item Libraries: flask, flask-restful, flask-cors, flask-jwt-extended, pandas
        \end{itemize}
    \item \textbf{PostgreSQL} for mission data and user storage
    \item \textbf{SQLAlchemy} ORM
\end{itemize}

\subsection*{Authentication}
\begin{itemize}
    \item JWT-based authentication using flask-jwt-extended
    \item bcrypt for password hashing
\end{itemize}

\subsection*{Deployment}
\begin{itemize}
    \item Docker and Docker Compose
    \item NGINX as reverse proxy
\end{itemize}

\section*{4. Required Packages and Dependencies}

\subsection*{Frontend (package.json)}
\begin{lstlisting}
{
  "dependencies": {
    "react": "^18.2.0",
    "react-dom": "^18.2.0",
    "react-router-dom": "^6.6.1",
    "axios": "^1.3.0",
    "bootstrap": "^5.2.3",
    "chart.js": "^4.2.1",
    "mapbox-gl": "^2.10.0"
  }
}
\end{lstlisting}

\subsection*{Backend (requirements.txt)}
\begin{lstlisting}
flask
flask-restful
flask-cors
flask-jwt-extended
sqlalchemy
pandas
bcrypt
psycopg2-binary
\end{lstlisting}

\section*{5. Docker Containers}
See accompanying docker-compose.yml for breakdown.

\end{document}
