
\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage[colorlinks=true,linkcolor=black,urlcolor=blue]{hyperref}
\usepackage{longtable}
\usepackage{array}
\usepackage{geometry}
\usepackage{tocloft}
\usepackage{fancyhdr}
\usepackage{lastpage}

\hypersetup{
    pdfborder={0 0 0},
    colorlinks=true,
    linkcolor=black,
    urlcolor=blue
}

\geometry{
  a4paper,
  left=1in,
  right=1in,
  top=1in,
  bottom=1in,
  headheight=14pt,
  headsep=0.5in,
  footskip=0.5in
}

\renewcommand{\cftsecleader}{\cftdotfill{\cftdotsep}}
\renewcommand{\cftsubsecleader}{\cftdotfill{\cftdotsep}}
\renewcommand{\cftsubsubsecleader}{\cftdotfill{\cftdotsep}}

\title{SUAS Software Design Document (SDD)}
\author{SUAS Development Team}
\date{May 2025}

\begin{document}

\maketitle
\newpage

\tableofcontents
\newpage

\section*{Version History}
\begin{longtable}{| m{3cm} | m{3cm} | m{8cm} |}
\hline
\textbf{Version} & \textbf{Date} & \textbf{Description} \\
\hline
1.0 & 2025-05-07 & Initial draft with Snapshots 1–4 integrated \\
\hline
0.9 & 2025-04-30 & Simulation environment added (Snapshot 3) \\
\hline
0.8 & 2025-03-30 & Navigation and pathfinding features added (Snapshot 2) \\
\hline
0.7 & 2025-02-28 & Core structure and modules completed (Snapshot 1) \\
\hline
\end{longtable}

\section{Introduction}
\subsection{Purpose}
This document outlines the software design for the SUAS (Software Unmanned Aircraft System) project.

\subsection{Intended Audience}
Developers, testers, stakeholders, and maintainers of the SUAS application.

\subsection{Overview}
This SDD includes a breakdown of architecture, user interface, and other design components of the system.

\section{System Architecture}
The system follows a modular architecture with separation between data processing, simulation logic, and front-end visualization.

\begin{itemize}
    \item \textbf{Backend:} Manages telemetry parsing, pathfinding, and mission execution.
    \item \textbf{Frontend:} Provides user interface for mission planning, navigation visualization, and simulation control.
    \item \textbf{Database:} Stores mission logs, UAV data, user preferences, and more.
\end{itemize}

\section{User Interface}
The user interacts with the application through a dashboard that shows:
\begin{itemize}
    \item Map interface for setting and viewing waypoints.
    \item Navigation controls and telemetry status.
    \item Simulated mission replay panel.
\end{itemize}

\subsection{Database Explanation}
PostgreSQL stores user-generated missions, system logs, and telemetry history.

\section{Glossary}
\begin{longtable}{| m{4cm} | m{10cm} |}
\hline
\textbf{Term} & \textbf{Definition} \\
\hline
SUAS & Software Unmanned Aircraft System \\
\hline
UAV & Unmanned Aerial Vehicle \\
\hline
UI & User Interface \\
\hline
API & Application Programming Interface \\
\hline
SRS & Software Requirements Specification \\
\hline
SDD & Software Design Document \\
\hline
\end{longtable}

\section{References}
\begin{itemize}
    \item \url{https://en.wikipedia.org/wiki/A*_search_algorithm}
    \item \url{https://docs.spring.io/spring-boot/docs/current/reference/html/}
    \item \url{https://postgis.net/}
    \item \url{https://www.chartjs.org/}
\end{itemize}

\end{document}
